---
always_allow_html: yes
---

# Appendix - Dictionary Tables{#tables}

```{r test_tables, echo=FALSE, message=FALSE}
source("example/R/fcn_documentation.R")

library(kableExtra)
library(dplyr)

options(kableExtra.html.bsTable = T)

```

This chapter shows the structure of all input or output csv-files that are referenced throughout the documentation. Please refer to the chapters for more detailed explanations.


## MTXQC base tables
### `config_mtx` tables

#### conv_filenames.csv{#app:filenames}
```{r cm01, echo=FALSE}
c1 = appendix_print("example/config_files/conv_filenames.csv")
c1 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)

# c01 = appendix_print("example/tables/config_conse.csv")
# c01 %>%
#    kable(escape = TRUE, booktabs = TRUE ) %>%
#    kable_styling(c("striped", "condensed"), 
#                  latex_options = "striped", 
#                  full_width = TRUE)

```

#### conv_filesnames_manVal.csv{#app:filenamesManVal}
```{r cm02, echo=FALSE}
c2 = appendix_print("example/config_files/conv_filenames_manVal.csv", 5)
c2 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### DEPRICATED FILE: MQ_correction.csv

Not in use anymore since fluffy adventure!

```{r cm03, echo=FALSE}
c3 = appendix_print("example/config_files/MQ_correction.csv")
c3 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```


### `config_files` tables

These tables are supposed to be modified in relation to the individual needs of a project.

#### conversion_metabolite.csv {#app:conse}
```{r cf_01, echo=FALSE}
t1 = appendix_print(path_def = "example/tables/config_conse.csv")

t1 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### letter_pathway_complete.csv{#app:pathway}
```{r cf_02, echo=FALSE}
t2 = appendix_print("example/config_mtx/letter_pathway_complete.csv", 4)
t2 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### incorp_calc_masses.csv{#app:incorp}
```{r cf_03, echo=FALSE}
t3 = appendix_print("example/config_mtx/incorp_calc_masses.csv", 5)
t3 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)

```

#### quant1_values.csv{#app:quant1}
```{r cf_04, echo=FALSE}
t4 = appendix_print("example/config_mtx/quant1_values.csv", 5)
t4 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### mid_backups.csv{#app:midbackup}
```{r cf_05, echo=FALSE}
t5 = appendix_print("example/config_mtx/mid_backups.csv", 10)
t5 %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

## Input data
### MAUI derived tables




### Metmax derived tables



## Output data

### Experimental Setup



### MTXQCvX2 part1

#### `output/gc/...`{#o_gc}
##### `HM_GC_values.csv` \& `qcmetric_xy.csv`

MTXQC exports a file summarising quality factors for each of the four parameter evaluating the GC performance. A summary representing the values illustrated in the heatmap are shown in table [`HM_GC_values.csv`](\@ref(tab:o_hm_gc)), individual exports for each metric in table [`qcmetric_xy.csv`](\@ref(tab:o_gc_metric)).

```{r o_hm_gc, echo=FALSE}

t = appendix_print("example/tables/output_HM_gc.csv")
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

```{r o_gc_metric, echo=FALSE}

t = appendix_print("example/tables/output_HM_gc.csv")
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```


##### `IntStandard_normfactors.csv` \& `IntStandard_stats.csv`

```{r o_is_normfactors, echo=FALSE}

t = appendix_print("example/tables/output_isnormfactors.csv")
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

```{r o_is_normstats, echo=FALSE}

t = appendix_print("example/tables/output_is_stats.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```


##### `Min_Annotation.csv` \& `SumArea_stats.csv`

```{r o_soa, echo=FALSE}

t = appendix_print("example/tables/output_gc_sumarea.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

```{r o_minann, echo=FALSE}

t = appendix_print("example/tables/output_minann.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `mz73_data.csv`

```{r o_mzz, echo=FALSE}

t = appendix_print("example/tables/output_mz72.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### `output/quant/...`{#o_quant}

##### `calcheck_linearity.csv`

```{r o_calcheck, echo=FALSE}

t = appendix_print("example/tables/quant_calcheck.csv",5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `CalculationFileData.csv`{#CalcFileData}

This is porbably the most important file that is generated by running `MTXQCvX2_part1.Rmd`. It summarises all quality factors, experimental data and determined quantities of your experiment. This file provides the input for `MTXQCvX2_part2-PostProcessing.Rmd`.

```{r o_calcfiledata, echo=FALSE}

t = appendix_print("example/tables/output_quant_calculationfiledata.csv", 10)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `HeatMap_Quant_pTop5.csv`

```{r o_hm_quant, echo=FALSE}

t = appendix_print("example/tables/output_hm_quant.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `pTop5_Calibration_Samples_lincheck.csv`

```{r o_quant_lincheck, echo=FALSE}

t = appendix_print("example/tables/output_quant_lincheck.csv", TRUE)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `top5_CalibrationInfo_unique.csv`

```{r o_quant_info, echo=FALSE}
t = appendix_print("example/tables/output_quant_calibrationInfo.csv",5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `top5_QMQcurveInfo.csv`

```{r o_quant_qmq, echo=FALSE}
t = appendix_print("example/tables/output_quant_qmq.csv")
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

#### `output/inc/...`{#o_inc}

##### `HeatMap_Incorporation.csv`

```{r o_inc_hm, echo=FALSE}
t = appendix_print("example/tables/output_inc_hm.csv", 5)
knitr::kable(t, booktabs = TRUE)
```

##### `SE_calculation_NAscore.csv`

```{r o_inc_calc, echo=FALSE}
t = appendix_print("example/tables/output_inc_SEcalc.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `SE_classification.csv`

```{r o_inc_class, echo=FALSE}
t = appendix_print("example/tables/output_inc_SEclass.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```

##### `SE_validation.csv`

```{r o_inc_eval, echo=FALSE}
t = appendix_print("example/tables/output_inc_SEval.csv", 5)
t %>%
   kable(escape = TRUE, booktabs = TRUE ) %>%
   kable_styling(c("striped", "condensed"), 
                 latex_options = "striped", 
                 full_width = TRUE)
```



#### MTXQCvX2 part3


#### MTXQCvX2 part4
